Benchmarking figures

### 2016-05-06 results/figures.Rmd
fixed bug in data handeling

```{r,lofreq,fig.height=5,fig.width=3.4}

lofreq.df<-read.csv("../data/process/2015-6-23/Lofreq/lofreq_csv/all.lofreq.csv",stringsAsFactors = F,comment.char="#")

lofreq.df<-mutate(lofreq.df,mutation=paste0(CHROM,"_",REF,POS,ALT))
lofreq.df<-mutate(lofreq.df,category=mutation %in% true_snv$mutant,Id=ID,chr=CHROM,pos=POS,freq.var=AF)
lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$category[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"
lofreq.df<-ddply(lofreq.df,~chr,primer.cut)

lofreq.df$p.val<-as.numeric(lofreq.df$QUAL) # to make the roc based on the quality scores given by lofreq
lofreq.df<-mutate(lofreq.df, gc = sub(pat,"\\1",Id),
       exp.freq = sub(pat,"\\2",Id)
)
mutate(lofreq.df,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->lofreq.df
lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")

@@

#knitr::kable(subset(lofreq.table,gc==5,select=c(exp.freq,TP,FP)))
lofreq.table<-subset(lofreq.table,gc==5,select=-c(gc,Id)) # don't need the 0.1% sample
rename(lofreq.table,c("exp.freq"="Frequency","TP"="True\nPositives","FP"="False\nPositives"))->lofreq.table
lofreq.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
lofreq.table$Sensitivity<-round(lofreq.table$Sensitivity,digits=dd)
lofreq.table$Specificity<-round(lofreq.table$Specificity,digits=dd)
lofreq.table<-subset(lofreq.table,select=c("Frequency","Sensitivity","True\nPositives","Specificity","False\nPositives"))
tt2<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.65,fontfamily="serif")),core=list(fg_params=list(cex=0.65,fontfamily="serif")))

@@

pdf("../results/figures/lofreq1.pdf",width=3.4,height=5)
ggdraw() +
  draw_plot(lofreq.roc.p, 0, 0.5, 0.9, 0.45) +
  draw_plot(tbl, 0.025, 0, 0.95, .48) +
  draw_plot_label(c("A", "B"), c(0, 0), c(1, 0.5), size = 15)
dev.off()

>>>>

```{r,lofreq,fig.height=5,fig.width=3.4}
lofreq.df<-read.csv("../data/process/2015-6-23/Lofreq/lofreq_csv/all.lofreq.csv",stringsAsFactors = F,comment.char="#")

lofreq.df<-rename(lofreq.df,c("CHROM"="chr",
                        "POS"="pos",
                        "ID"="Id",
                        "REF"="ref",
                        "ALT"="var",
                        "AF"="freq.var"
))

lofreq.df<-mutate(lofreq.df,mutation=paste0(chr,"_",ref,pos,var))#,category=mutation %in% tp$mutant)->lofreq.df

#lofreq.df$Id[lofreq.df$Id=="3_03"]<-"3_02" # correct a naming error

WT<-subset(lofreq.df,grepl("WT",Id)) # Separate WT samples 
lofreq.df<-subset(lofreq.df,!(grepl("WT",Id))& Id!="Plasmid_control")

#lofreq.df<-mutate(lofreq.df,p.val=10^(QUAL/-10))

pat<-"([0-9]+)_([0-9]+)"
mutate(lofreq.df, gc = sub(pat,"\\1",Id),
       exp.freq = sub(pat,"\\2",Id)
)-> lofreq.df
mutate(lofreq.df,exp.freq=ifelse(test = grepl("0",exp.freq),yes=as.numeric(exp.freq)/1000,no = as.numeric(exp.freq)/100))->lofreq.df

# TF column
lofreq.df<-mutate(lofreq.df,category=mutation %in% true_snv$mutant) # add Column for True and false variants
wt1_mut<-subset(WT,Id=="WT1",select=mutation)
wt2_mut<-subset(WT,Id=="WT2",select=mutation)

length(wt_mut)
lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"

lofreq.df$category[lofreq.df$mutation %in% wt_mut]<-"wt"
lofreq.df$categroy[lofreq.df$mutation %in% mfe.df$mutation]<-"mfe"

lofreq.df$p.val<-lofreq.df$QUAL # to make the roc based on the quality scores given by lofreq

lofreq.roc<-hiseq.roc(lofreq.df,possible_tp,possible_vars,"<")

@@

lofreq.table<-subset(lofreq.table,gc==5,select=-c(gc,Id)) # don't need the 0.1% sample
rename(lofreq.table,c("exp.freq"="Frequency","TP"="True\nPositives","FP"="False\nPositives"))->lofreq.table
lofreq.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
lofreq.table$Sensitivity<-round(lofreq.table$Sensitivity,digits=dd)
lofreq.table$Specificity<-round(lofreq.table$Specificity,digits=dd)
lofreq.table<-subset(lofreq.table,select=c("Frequency","Sensitivity","True\nPositives","Specificity","False\nPositives"))

tt2<-ttheme_minimal(colhead=list(fg_params=list(fontface=1,cex=0.65,fontfamily="serif")),core=list(fg_params=list(cex=0.65,fontfamily="serif")))

@@

# pdf("../results/figures/lofreq1.pdf",width=3.4,height=5)
# ggdraw() +
#   draw_plot(lofreq.roc.p, 0, 0.5, 0.9, 0.45) +
#   draw_plot(tbl, 0.025, 0, 0.95, .48) +
#   draw_plot_label(c("A", "B"), c(0, 0), c(1, 0.5), size = 15)
# dev.off()
